\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation; the contributions prior to Rev0 are
NOT included.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 6\\
Leo Vugert & 6\\
Nathan Perry & 6\\
Tim Pokanai & 6\\
Aidan Goodyer & 6\\
Jeremy Orr & 6\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } [Dr. Henry Szechtman and Dr.Anna Dvorkin-Gheva]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Jeremy Orr & 5\\
Nathan Perry & 5\\
Tim Pokanai & 5\\
Leo Vugert & 5\\
Aidan Goodyer & 5\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Jeremy Orr & 0\\
Nathan Perry & 0\\
Tim Pokanai & 0\\
Leo Vugert & 0\\
Aidan Goodyer & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } [Tiago de Moraes Machado]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Jeremy Orr & 1\\
Nathan Perry & 1\\
Tim Pokanai & 1\\
Leo Vugert & 1\\
Aidan Goodyer & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 83 & 100\% \\
Nathan Perry & 40 & 48.2\% \\
Aidan Goodyer & 17 & 20.5\% \\
Tim Pokanai & 7 & 8.4\% \\
Jeremy Orr & 7 & 8.4\% \\
Leo Vugert & 12 & 14.5\% \\
\bottomrule
\end{tabular}
\end{table}

Many commits and features haven't been pushed to the repo yet, so these numbers are not final.  The team is working on
pushing all commits and features before the final demo.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Leo Vugert & 10 & 3 \\
Nathan Perry & 1 & 7 \\
Aidan Goodyer & 2 & 1 \\
Tim Pokanai & 2 & 2 \\
Jeremy Orr & 1 & 1 \\
\bottomrule
\end{tabular}
\end{table}

Issues were mainly made for the VnV Report.


\section{Team Charter Trigger Items}

\subsection{Trigger Items}
\begin{enumerate}
    \item{Team member misses meeting without providing notice or reason}
    \item{Team member misses meeting without providing an acceptable excuse}
    \item{Team member's contributions do not hold up to the scrutiny of a peer review}
    \item{Team member's contributions do not hold up to the team's final document review}
    \item{Team member's attitude during meetings or discussion is detrimental to the team environment}
    \item{Team member does not contribute their fair share of issues in the Kanban board}
\end{enumerate}

\subsection{Violations}

\par{Refer to above section for corresponding trigger items. The violations will
be summarized anonymously.}
\begin{enumerate}
    \item{0 violation.}
    \item{0 violation.}
    \item{2 violations. Forgot to submit peer reviews for the VnV Report.}
    \item{0 violation.}
    \item{2 violations. Lack of seriousness in internal meeting, causing unproductive discussions and going over meeting time.}
    \item{0 violations.}
\end{enumerate}

\subsection{Violation Plan}

\par{Refer to above sections for violation and trigger information}

\begin{enumerate}
    \item{N/A}
    \item{N/A}
    \item{Communicate with team members about peer review expectations. Peer reviews should be taken seriously, otherwise our grades take a hit and the pother team doesn't get much helpful feedback.}
    \item{N/A}
    \item{Communicate with team members about meeting expectations. Meetings should be taken seriously,
    otherwise we are just wasting each other's time.}
    \item{N/A}
\end{enumerate}

\section{Additional Productivity Metrics}

N/A

\end{document}