\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the PoC demo and the Rev
0 demo; the contributions prior to the PoC are NOT included.

\section{Demo Plans}

\begin{itemize}

    \item {\textbf{Data Visualizations: } Implemented a data visualization system tab
     for bar chart generation, a selection UI for future chart types, and an 
     interactive UI for user to configure options and metrics. }
    \item {\textbf{Natural Language Improvements: } Continued integration of LLM-based 
    query generation and response for improved user interactions. }
    \item {\textbf{Docker: } Established robust Docker containerization
     for reproducible development and production 
    deployments across team members' machines. }

\end{itemize}

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Leo Vugert & 2\\
Nathan Perry & 2\\
Tim Pokanai & 2\\
Aidan Goodyer & 2\\
Jeremy Orr & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } [Dr. Henry Szechtman and Dr.Anna Dvorkin-Gheva]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 1\\
Jeremy Orr & 1\\
Nathan Perry & 1\\
Tim Pokanai & 0\\
Leo Vugert & 1\\
Aidan Goodyer & 1\\
\bottomrule
\end{tabular}
\end{table}

Tim was unable to make the meeting as he was away on a trip. Our supervisor has been very
busy and we have not been able to schedule another meeting with him since the last one.
Weekly meetings will continue next week.

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Jeremy Orr & 0\\
Nathan Perry & 0\\
Tim Pokanai & 0\\
Leo Vugert & 1\\
Aidan Goodyer & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } [Tiago de Moraes Machado]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 0\\
Jeremy Orr & 0\\
Nathan Perry & 0\\
Tim Pokanai & 0\\
Leo Vugert & 0\\
Aidan Goodyer & 0\\
\bottomrule
\end{tabular}
\end{table}

No TA meeting due to snow day.

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 26 & 100\% \\
Nathan Perry & 9 & 34.6\% \\
Aidan Goodyer & 11 & 42.3\% \\
Tim Pokanai & 1 & 3.8\% \\
Jeremy Orr & 2 & 7.7\% \\
Leo Vugert & 3 & 11.5\% \\
\bottomrule
\end{tabular}
\end{table}

Tim has unaccounted commits from the module implementation assignment, where he commited
changes to the Team 4's repo. Tim and Leo also have unnaccounted commits from unmerged
changes for data visualizations. Nathan has unnaccounted commits from an unmerged change 
for the inventory page.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Leo Vugert & 2 & 0 \\
Nathan Perry & 0 & 0 \\
Aidan Goodyer & 3 & 0 \\
Tim Pokanai & 1 & 0 \\
Jeremy Orr & 1 & 1 \\
\bottomrule
\end{tabular}
\end{table}

Nathan has also been working on issues as well as trying to bring the professors vision
for an "Inventory" page to life.

\section{CICD}

Our project utilizes GitHub Actions to implement a robust CI/CD pipeline consisting 
of three parallel workflows that handle security, documentation, and deployment.

\begin{itemize}
    \item \textbf{Automated Security Scanning (CodeQL):} 
    To ensure code quality, the CodeQL Advanced workflow triggers on every 
    push and pull request to the main branch. It employs GitHub's CodeQL engine to 
    perform static analysis on Python, JavaScript, and TypeScript files, identifying 
    security vulnerabilities before code is merged.

    \item \textbf{Documentation as Code (buildtex):} 
    Documentation is automatically compiled using the buildtex workflow. 
    When changes are detected in the docs directory, the pipeline initiates a
     TeXLive 2024 environment to compile modified \LaTeX\ files into PDFs. These PDFs
      are then automatically committed back to the repository, ensuring documentation 
      remains synchronized with the source.

    \item \textbf{Continuous Deployment (Self-Hosted):} 
    The \texttt{Deploy RatBat2} workflow executes on a self-hosted runner 
    directly on our production server. Upon a push to main, the pipeline injects 
    secrets and uses Docker Compose to rebuild the application containers. 
    The script includes conditional logic to deploy a Production environment
     (ports 80/443) for the main branch, or a Staging environment 
     (ports 8080/8001) for development branches.
\end{itemize}

\section{Team Charter Trigger Items}

\subsection{Trigger Items}
\begin{enumerate}
    \item{Team member misses meeting without providing notice or reason}
    \item{Team member misses meeting without providing an acceptable excuse}
    \item{Team member's contributions do not hold up to the scrutiny of a peer review}
    \item{Team member's contributions do not hold up to the team's final document review}
    \item{Team member's attitude during meetings or discussion is detrimental to the team environment}
    \item{Team member does not contribute their fair share of issues in the Kanban board}
\end{enumerate}

\subsection{Violations}

\par{Refer to above section for corresponding trigger items. The violations will
be summarized anonymously.}
\begin{enumerate}
    \item{0 violation.}
    \item{0 violations}
    \item{0 violations.}
    \item{0 violation.}
    \item{1 violation. Lack of seriousness in internal meeting, causing unproductive discussions and going over meeting time.}
    \item{0 violations.}
\end{enumerate}

\subsection{Violation Plan}

\par{Refer to above sections for violation and trigger information}

\begin{enumerate}
    \item{N/A}
    \item{N/A}
    \item{N/A}
    \item{N/A}
    \item{Communicate with team members about meeting expectations. Meetings should be taken seriously,
    otherwise we are just wasting each other's time.}
    \item{N/A}
\end{enumerate}

\section{Additional Productivity Metrics}

N/A

\end{document}